When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2018-02-19 paper/paper.tex
Cite ER

Throughout, our graphs are undirected, and do not have any loops. In some cases vertices have
labels, which are treated as integers; we write $\ell(v)$ for the label of vertex $v$. Two vertices
are \emph{adjacent} if there is an edge between them. The \emph{neighbourhood} of a vertex is the
set of vertices to which it is adjacent, and the \emph{degree} of a vertex is the cardinality of its
neighbourhood. The \emph{order} of a graph is the cardinality of its vertex set. We write
$\operatorname{V}(G)$ for the vertex set of a graph $G$. The \emph{complement} of a graph $G$,
denoted $\shortoverline{G}$, is the graph with the same vertex set as $G$, and with an edge between
distinct vertices $v$ and $w$ if and only if $v$ and $w$ are not adjacent in $G$. We write $G(n, p)$
for an Erd\H{o}s-R\'enyi random graph with $n$ vertices, and an edge between each distinct unordered
pair of vertices with independent probability $p$.

>>>>

Throughout, our graphs are undirected, and do not have any loops. In some cases vertices have
labels, which are treated as integers; we write $\ell(v)$ for the label of vertex $v$. Two vertices
are \emph{adjacent} if there is an edge between them. The \emph{neighbourhood} of a vertex is the
set of vertices to which it is adjacent, and the \emph{degree} of a vertex is the cardinality of its
neighbourhood. The \emph{order} of a graph is the cardinality of its vertex set. We write
$\operatorname{V}(G)$ for the vertex set of a graph $G$. The \emph{complement} of a graph $G$,
denoted $\shortoverline{G}$, is the graph with the same vertex set as $G$, and with an edge between
distinct vertices $v$ and $w$ if and only if $v$ and $w$ are not adjacent in $G$.

An \emph{Erd\H{o}s-R\'enyi random graph}, written $G(n, p)$, is a graph with $n$ vertices, and an
edge between each distinct unordered pair of vertices with independent probability $p$
\citep{o:Gilbert59,o:ErdosR59}.\footnote{Note that elsewhere, this same name sometimes instead
refers to a graph $G(n, E)$ chosen uniformly from among all graphs with $n$ vertices and exactly $E$
edges.}
